Estimation of Spatiotemporal Integro-Difference Equations for Dynamical Neural Field Models

### 2009-11-17 ltx/BrainIDE.tex
Attempted to make a derivation of state-space formulation for a general nonlinearity (needs checking)

>>>>

\subsection{State-Space Model Alternative Approach}
First we define

\begin{eqnarray}
% \nonumber to remove numbering (before each equation)
  {v_{t + 1}}\left( r \right) &=& \int_\Omega  {k\left( {r - r'} \right)p\left( {{v_t}\left( {r'} \right)} \right) - \alpha v\left( {r,t} \right)dr'}  + \varepsilon \left( {r,t} \right) \\
   &=& \int_\Omega  {k\left( {r - r'} \right)p\left( {{v_t}\left( {r'} \right)} \right)dr'}  - \alpha v\left( {r,t} \right) + \varepsilon \left( {r,t} \right)
\end{eqnarray}

Defining
\begin{equation}\label{Def1}
   {v_t}\left( r \right) = {\phi ^T}\left( r \right){x_t}
\end{equation}
\begin{equation}\label{Def2}
k\left( {r - r'} \right) = {\theta ^T}\psi \left( {r - r'} \right)
\end{equation}
Since we assume knowledge of $\phi(r')$ and $p(.)$, and $\phi(r')$ is independent of $x_t$ we can uniquely define the functions $\kappa(.)$ and $\rho(.)$ such that
\begin{eqnarray}
% \nonumber to remove numbering (before each equation)
  p\left( {{v_t}\left( {r'} \right)} \right)  &=& p\left( {{\phi ^T}\left( {r'} \right){x_t}} \right) \\
   &=& \kappa \left( {{\phi ^T}\left( {r'} \right)} \right)\rho \left( {{x_t}} \right) 
\end{eqnarray}
Making substitutions we get
\begin{equation}\label{Subs}
{\phi ^T}\left( r \right){x_{t + 1}} = {\theta ^T}\int_\Omega  {\psi \left( {r - r'} \right)\kappa \left( {{\phi ^T}\left( {r'} \right)} \right)dr'} \rho \left( {{x_t}} \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon \left( {r,t} \right)
\end{equation}
now defining
\begin{equation}\label{Def4}
\Phi \left( r \right) = \int_\Omega  {\psi \left( {r - r'} \right)\kappa \left( {{\phi ^T}\left( {r'} \right)} \right)dr'}
\end{equation}
\begin{equation}\label{Sub2}
{\phi ^T}\left( r \right){x_{t + 1}} = {\theta ^T}\Phi \left( r \right)\rho \left( {{x_t}} \right) - \alpha {\phi ^T}\left( r \right){x_t} + \varepsilon \left( {r,t} \right)
\end{equation}
cross multiply in integrate over $r'$
\begin{equation}\label{CorssMultAndInt}
\int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_{t + 1}} = {\theta ^T}\int_\Omega  {\phi \left( r \right)\Phi \left( r \right)dr} \rho \left( {{x_t}} \right) - \alpha \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} {x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}
\end{equation}
Now we define
\begin{equation}\label{Def5}
{\Psi _x} = \int_\Omega  {\phi \left( r \right){\phi ^T}\left( r \right)dr} 
\end{equation}
\begin{equation}\label{Def6}
{\Psi _\theta } = \int_\Omega  {\phi \left( r \right)\Phi \left( r \right)dr}
\end{equation}
Making substitutions
\begin{equation}\label{Subs3}
{\Psi _x}{x_{t + 1}} = {\theta ^T}{\Psi _\theta }\rho \left( {{x_t}} \right) - \alpha {\Psi _x}{x_t} + \int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}
\end{equation}
Now we isolate the state by inverting $\Psi_x$
\begin{equation}\label{IsolateState}
{x_{t + 1}} = {\Psi _x}^{ - 1}{\theta ^T}{\Psi _\theta }\rho \left( {{x_t}} \right) - \alpha {x_t} + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}
\end{equation}
Gives the state-space model
\begin{equation}\label{StateSpaceModel}
{x_{t + 1}} = f\left( {x,\theta } \right) + {\Psi _x}^{ - 1}\int_\Omega  {\phi \left( r \right)\varepsilon \left( {r,t} \right)dr}
\end{equation}
